\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2014-05-22 doc/sw-system.tex
Planned crowd results section with Baumer

Enthusiasm: histogram of classifications, stage 1 vs stage 2. Information
contributed. Correlation with number of classifications.

PL and PD as measures of skill. not quite talent, due to possibility of
learning - but agents assume talent. Performance of crowd re PD and PL.
Correlations with N classifications.

>>>>

% Enthusiasm: histogram of classifications, stage 1 vs stage 2. Information
% contributed. Correlation with number of classifications. 
% 
% PL and PD as measures of skill. not quite talent, due to possibility of
% learning - but agents assume talent. Performance of crowd re PD and PL.
% Correlations with N classifications.

What are the properties of the crowd? Corner plots: skill, effort, combine to
give contribution. Actual information generated. Making your own luck. How do these depend on
experience (no. of training images). Describe plot features, in stage 1.
Contrast with stage 2. \Fref{fig:crowd:cornerplot}

Who's doing all the work?
Cumulative plot of ``contributions'' (applied skill).
\Fref{fig:crowd:cumulplot}

Information, contribution totals and their interpretation. Inefficiency
measures? Super-users. 
\Tref{tab:crowd:contributions} shows contributions at stage 2 and stage 1

Can we predict skill? Early skill vs final skill - some correlation,
especially in high skill users, but very broad distribution though: not
possible to predict.
\Fref{fig:crowd:skillprediction}

Stage 1 skill vs Stage 2 skill. 
Who continued to do Stage 2? Numbers. 
\Fref{fig:crowd:stage1vstage2}
